Aligning species range data to better serve science and conservation

### 2015-12-29 data_explore/data_explore.Rmd
data_explore updates

setwd('data_explore')
source('data_explore_fxns.R')
### When knitting this, it automatically sets WD to be this directory...
### the 'setwd()' is there for running by chunk
```

@@

```{r get_spp_list, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}
### this file created in data_prep
read.csv(spp_list, file.path(dir_data, 'spp_list_w_area_trimmed.csv'), stringsAsFactors = FALSE)

@@

scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  labs(x = bquote('Extent alignment '*alpha['ext']*' (%)'), 
       y = bquote('Distribution alignment '*alpha['dist']*' (%)'), 
       title = 'Distribution alignment vs Extent alignment',
       color = 'Risk', size = '% ocean range')

@@

spp_list_quads <- spp_list1 %>%
  mutate(quad = NA,
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q1$sciname, 'q1', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q2$sciname, 'q2', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q3$sciname, 'q3', quad),
         quad = ifelse(is.na(quad) & sciname %in% spp_list_q4$sciname, 'q4', quad))
write.csv(spp_list_quads, file.path(dir_data, 'spp_list_quads.csv'), row.names = FALSE)

@@

write.csv(spp_gp_quadrants, file.path(dir_data, 'spp_gp_quads.csv'), row.names = FALSE)

@@

>>>>

setwd('data_explore') 
  ### When knitting, it automatically sets WD to be this directory...
  ### this command is just here to facilitate running when not in knit mode.
source('data_explore_fxns.R')
```

@@

```{r get_spp_list, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}
data_file <- file.path(dir_data, 'spp_list_w_area_all.csv')

if (!file.exists(data_file)) {
  ### species info list - scinames, IUCN species ID, AM species ID, category etc
  spp_list_base <- read.csv(file.path(dir_data, 'spp_am_v_iucn.csv'),
                            stringsAsFactors = FALSE)

  create_spp_list(spp_list_base, data_file)
}

spp_list <- read.csv(data_file, stringsAsFactors = FALSE) 
### At this point, spp_list contains subpops and aliases, and zero-area IUCNs

spp_list <- spp_list %>%
  filter(!is.na(sm_perc)) %>%
  ### will ditch the ones where no IUCN polygon exists - or are these species
  ### whose ranges only occur in cells beyond the LOICZID grid?
  filter(!str_detect(spatial_source, 'subpop') & !str_detect(spatial_source, 'alias'))
spp_list <- spp_list %>%
  left_join(read.csv(file.path(dir_data, 'sciname_lookups/spp_groupnames.csv'), 
                     stringsAsFactors = FALSE),
            by = 'spp_group')

write.csv(spp_list, file.path(dir_data, 'spp_list_w_area_trimmed.csv'))

@@

scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  labs(x = bquote('Area alignment '*alpha['area']*' (%)'), 
       y = bquote('Distribution alignment '*alpha['dist']*' (%)'), 
       title = 'Distribution alignment vs area alignment',
       color = 'Risk', size = '% ocean range')

@@

@@

@@

spp_list1 <- spp_list %>%
  group_by(popn_category) %>%
  mutate(n_spp = n()) %>%
  ungroup()

### 2015-12-29 ms_0_main.Rmd
data_explore updates

---
title: "Aligning species range data to better serve science and conservation"
author: "Casey O'Hara, Jamie Afflerbach, Ben Halpern"
output:
  pdf_document:
    number_sections: yes
    toc: no
  html_document:
    highlight: haddock
    number_sections: yes
    theme: spacelab
    toc: yes
  word_document: default
---

>>>>

---
title: "Aligning species range data to better serve science and conservation"
author: "Casey O'Hara, Jamie Afflerbach, Ben Halpern"
output:
  html_document:
    highlight: haddock
    number_sections: yes
    theme: spacelab
    toc: yes
  pdf_document:
    number_sections: yes
    toc: no
  word_document: null
---
